On particular examples of planar integral point sets and their classification \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2021-02-24 AvdMomZvolA_examples/ips_examples.tex
[AMZAE] Transitional commit: prepare the first version to be submitted

\usepackage[backend=biber,style=gost-numeric,sorting=none]{biblatex}
\addbibresource{../common/notmy.bib}
\addbibresource{../common/my.bib}

\usepackage{hyperref}

@@

The set on Fig. TODO has been obtained from the set on Fig. TODO by dilation by 5.

The set on Fig. TODO has been obtained from the set on Fig. TODO by dilation by 42 (or less? TODO).

\section{Arrow-like integral point sets with one axis of symmetry}

TODO:

на каждое такое множество: исходный вариант, все этапы растращаивания с коэффициентом растаращивания и пояснением, кто из кого.

@@

\printbibliography

>>>>

%\usepackage[backend=biber,style=gost-numeric,sorting=none]{biblatex}
%\addbibresource{../common/notmy.bib}
%\addbibresource{../common/my.bib}
%\usepackage{../../../biblatex2bibitem/biblatex2bibitem}

\usepackage{hyperref}
\usepackage{cite}

@@

%The set on Fig. TODO has been obtained from the set on Fig. TODO by dilation by 5.

%The set on Fig. TODO has been obtained from the set on Fig. TODO by dilation by 42 (or less? TODO).

%\section{Arrow-like integral point sets with one axis of symmetry}

%на каждое такое множество: исходный вариант, все этапы растращаивания с коэффициентом растаращивания и пояснением, кто из кого.

@@

%\printbibliography
%\printbibitembibliography

\begin{thebibliography}{99}
%
\bibitem{anning1945integral}
\emph{Anning} \emph{N. H.}, \emph{Erdős} \emph{P.}. Integral distances //
Bulletin of the American Mathematical Society. — 1945. — Vol. 51, no. 8. —
Pp. 598–600. — DOI: \href {https://doi.org/10.1090/S0002-9904-1945-08407-9}
{\nolinkurl {10.1090/S0002-9904-1945-08407-9}}.
%
\bibitem{erdos1945integral}
\emph{Erdős} \emph{P.}. Integral distances // Bulletin of the American Mathematical
Society. — 1945. — Vol. 51, no. 12. — P. 996. — DOI: \href
{https://doi.org/10.1090/S0002-9904-1945-08490-0} {\nolinkurl
{10.1090/S0002-9904-1945-08490-0}}.%
\bibitem{kemnitz1988punktmengen}
\emph{Kemnitz} \emph{A.}. Punktmengen mit ganzzahligen Abständen. — 1988.
%
\bibitem{kurz2005characteristic}
\emph{Kurz} \emph{S.}. On the characteristic of integral point sets in {$\mathbb
{E}^m$} // Australasian Journal of Combinatorics. — 2006. — Vol. 36. —
Pp. 241–248. — arXiv: \href {http://arxiv.org/abs/math/0511704} {\nolinkurl
{math/0511704}}.
%
\bibitem{kurz2008minimum}
\emph{Kurz} \emph{S.}, \emph{Wassermann} \emph{A.}. On the minimum diameter
of plane integral point sets // Ars Combinatoria. — 2011. — Vol. 101. — Pp. 265–287. —
arXiv: \href {http://arxiv.org/abs/0804.1307} {\nolinkurl {0804.1307}}.
%
\bibitem{solymosi2003note}
\emph{Solymosi} \emph{J.}. Note on integral distances // Discrete \& Computational
Geometry. — 2003. — Vol. 30, no. 2. — Pp. 337–342. — DOI: \href
{https://doi.org/10.1007/s00454-003-0014-7} {\nolinkurl {10.1007/s00454-003-0014-7}}.
%
\bibitem{kreisel2008heptagon}
\emph{Kreisel} \emph{T.}, \emph{Kurz} \emph{S.}. There are integral heptagons, no
three points on a line, no four on a circle // Discrete \& Computational Geometry. —
2008. — Vol. 39, no. 4. — Pp. 786–790. — DOI: \href
{https://doi.org/10.1007/s00454-007-9038-6} {\nolinkurl {10.1007/s00454-007-9038-6}}.
%
\bibitem{our-ped-2018}
\emph{Авдеев} \emph{Н. Н.}. On integral point sets in special position // Некоторые
вопросы анализа, алгебры, геометрии и математического образования: материалы
международной молодежной научной школы «Актуальные направления
математического анализа и смежные вопросы». — 2018. — Vol. 8. — Pp. 5–6.
%
\bibitem{our-pmm-2018}
\emph{Авдеев} \emph{Н. Н.}. Об отыскании целоудалённых множеств
специального вида // Актуальные проблемы прикладной математики,
информатики и механики - сборник трудов Международной научной
конференции. — Научно-исследовательские публикации, 2018. — Pp. 492–498.
%
\bibitem{our-vmmsh-2018}
\emph{Авдеев} \emph{Н. Н.}, \emph{Семёнов} \emph{Е. М.}. Множества точек с
целочисленными расстояниями на плоскости и в евклидовом пространстве //
Математический форум (Итоги науки. Юг России). — 2018. — Pp. 217–236.%
\bibitem{our-vmmsh-2018-translit}
\emph{Avdeev} \emph{N. N.}, \emph{Semenov} \emph{E. M.}. Integral point sets in
the plane and Euclidean space (Множества точек с целочисленными расстояниями
на плоскости и в евклидовом пространстве) // Matematicheskij forum (Itogi nauki.
Yug Rossii). — 2018. — Pp. 217–236.
%
\bibitem{avdeev2019particular}
\emph{Avdeev} \emph{N. N.}, \emph{Zvolinsky} \emph{R. E.},
\emph{Momot} \emph{E. A.}. On particular diameter bounds for integral point sets in
higher dimensions. — 2019. — arXiv: \href {http://arxiv.org/abs/1909.10386}
{\nolinkurl {1909.10386}}. — URL: \url
{https://ui.adsabs.harvard.edu/abs/2019arXiv190910386A/abstract}.
%
\bibitem{kurz2013constructing}
Constructing $7$-clusters / S. Kurz [et al.] // Serdica Journal of Computing. — 2014. —
Vol. 8, no. 1. — Pp. 47–70. — arXiv: \href {http://arxiv.org/abs/1312.2318} {\nolinkurl
{1312.2318}}.
%
\bibitem{antonov2008maximal}
\emph{Antonov} \emph{A. R.}, \emph{Kurz} \emph{S.}. Maximal integral point sets
over {$\mathbb {Z}^2$} // International Journal of Computer Mathematics. —
2008. — Vol. 87, no. 12. — Pp. 2653–2676. — DOI: \href
{https://doi.org/10.1080/00207160902993636} {\nolinkurl
{10.1080/00207160902993636}}. — arXiv: \href {http://arxiv.org/abs/0804.1280}
{\nolinkurl {0804.1280}}.
%
\bibitem{solymosi2010question}
\emph{Solymosi} \emph{J.}, \emph{De Zeeuw} \emph{F.}. On a question of Erdős
and Ulam // Discrete \& Computational Geometry. — 2010. — Vol. 43, no. 2. —
Pp. 393–401. — arXiv: \href {http://arxiv.org/abs/0806.3095} {\nolinkurl
{0806.3095}}.
\end{thebibliography}
